### 2024-02-04 docs/projects/noj/ggplot.qmd
Noj -rerendered

# Exploring ggplot

@@

<g id="surface6">

@@

Trying to mimic [cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list (WIP):

::: {.sourceClojure}
```clojure
(let [f (-> plot
            (r$ 'facet)
            (r$ 'params)
            (r$ 'facets))]
  (when (-> `(is.null ~f)
            r
            r->clj)
    (let [facet (-> `(ls ~f)
                    r
                    (r->clj)
                    first)]
      {:facet facet
       :facet-levels (-> plot
                         (r$ 'data)
                         (r/bra facet))})))
```
:::

::: {.printedClojure}
```clojure
{:facet "cyl", :facet-levels # A tibble: 234 × 1
     cyl
   &lt;int&gt;
 1     4
 2     4
 3     4
 4     4
 5     6
 6     6
 7     6
 8     4
 9     4
10     4
# ℹ 224 more rows
}

>>>>

# Exploring ggplot
following
[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list
in representing a plot as a data structure.

@@

<g id="surface11">

@@

::: {.sourceClojure}
```clojure
(defn gg-facet [ggplot]
  (let [f (-> ggplot
              (r$ 'facet)
              (r$ 'params)
              (r$ 'facets))]
    (when (-> `(is.null ~f)
              r
              r->clj)
      (let [facet (r `(ls ~f))]
        {:facet facet
         :facet-levels (-> plot
                           (r$ 'data)
                           (r/bra facet))}))))
```
:::

::: {.sourceClojure}
```clojure
(-> plot
    gg-facet
    (update-vals r->clj))
```
:::

<div style="max-height:600px;overflow-y:auto;"><div><p>{</p><div style="margin-left:10%;width:110%;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet ["cyl"]</code></pre></div><table><tr><td valign="top"><div style="max-height:600px;overflow-y:auto;"><div><pre><code class="sourceCode language-clojure printed-clojure">:facet-levels
</code></pre></div></div></td><td><div style="margin-left:10px;"><div><p>_unnamed \[234 1\]:</p><table class="table"><thead><tr><th style="text-align:right;">:cyl</th></tr></thead><tbody><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">...</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">5</td></tr><tr><td style="text-align:right;">5</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">4</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr><tr><td style="text-align:right;">6</td></tr></tbody></table></div></div></td></tr></table></div><p>}</p></div></div>

::: {.sourceClojure}
```clojure
(r/require-r '[base])
```
:::

::: {.printedClojure}
```clojure
nil

::: {.sourceClojure}
```clojure
(defn ->clj
  ([r-obj avoid]
   (->clj r-obj avoid []))
  ([r-obj avoid path]
   (prn path)
   (let [relevant-names (some->> r-obj
                                 r.base/names
                                 r->clj
                                 (filter (complement avoid)))]
     (cond
       ;;
       ;; a named list or a ggproto object
       (seq relevant-names) (->> relevant-names
                                 (map (fn [nam]
                                        [(keyword nam) (-> r-obj
                                                           (r$ nam)
                                                           (->clj avoid
                                                                  (conj path nam)))]))
                                 (into {}))
       ;;
       ;; a ggproto method
       (-> r-obj
           r.base/class
           r->clj
           first
           (= "ggproto_method"))
       :ggproto-method
       ;;
       ;; an unnamed list
       (-> r-obj
           r.base/is-list
           r->clj
           first)
       (-> r-obj
           r.base/length
           r->clj
           first
           range
           (->> (mapv (fn [i]
                        (prn [path (inc i)])
                        (-> r-obj
                            (r/brabra (inc i))
                            (->clj avoid
                                   (conj path [i])))))))
       ;;
       (r.base/is-function r-obj) :function
       (r.base/is-atomic r-obj) (r->clj r-obj)
       :else r-obj))))
```
:::

::: {.sourceClojure}
```clojure
(-> plot
    (->clj #{"data" "plot_env"}))
```
:::

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend :function,
   :mapping :function,
   :super :ggproto-method,
   :computed_stat_params {:na.rm :function},
   :inherit.aes :function,
   :geom_params {:na.rm :function},
   :geom
   {:non_missing_aes :function,
    :draw_key :ggproto-method,
    :default_aes
    {:shape :function,
     :colour :function,
     :size :function,
     :fill :function,
     :alpha :function,
     :stroke :function},
    :super :ggproto-method,
    :required_aes :function,
    :draw_panel :ggproto-method},
   :stat_params {:na.rm :function},
   :constructor :function,
   :computed_mapping {:x :function, :y :function, :colour :function},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :computed_geom_params {:na.rm :function}}
  {:aes_params [],
   :stat
   {:extra_params :function,
    :super :ggproto-method,
    :compute_group :ggproto-method,
    :required_aes :function,
    :setup_params :ggproto-method,
    :dropped_aes :function},
   :show.legend :function,
   :mapping :function,
   :super :ggproto-method,
   :computed_stat_params
   {:na.rm :function,
    :method :function,
    :n :function,
    :orientation :function,
    :level :function,
    :fullrange :function,
    :flipped_aes :function,
    :se :function,
    :formula :function,
    :method.args [],
    :span :function},
   :inherit.aes :function,
   :geom_params
   {:se :function, :na.rm :function, :orientation :function},
   :geom
   {:setup_params :ggproto-method,
    :super :ggproto-method,
    :draw_key :ggproto-method,
    :extra_params :function,
    :required_aes :function,
    :draw_group :ggproto-method,
    :optional_aes :function,
    :rename_size :function,
    :setup_data :ggproto-method,
    :default_aes
    {:colour :function,
     :fill :function,
     :linewidth :function,
     :linetype :function,
     :weight :function,
     :alpha :function}},
   :stat_params
   {:na.rm :function,
    :method :function,
    :n :function,
    :orientation :function,
    :level :function,
    :fullrange :function,
    :se :function,
    :formula :function,
    :method.args [],
    :span :function},
   :constructor {: :function, :method :function},
   :computed_mapping {:x :function, :y :function, :colour :function},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :computed_geom_params
   {:se :function,
    :na.rm :function,
    :orientation :function,
    :flipped_aes :function}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x :function, :y :function, :colour :function},
 :theme [],
 :coordinates
 {:expand :function,
  :clip :function,
  :limits {:x :function, :y :function},
  :super :ggproto-method,
  :default :function},
 :facet
 {:params
  {:dir :function,
   :nrow :function,
   :as.table :function,
   :free {:x :function, :y :function},
   :drop :function,
   :strip.position :function,
   :ncol :function,
   :facets {:cyl :function},
   :labeller :function},
  :shrink :function,
  :super :ggproto-method},
 :labels {:x :function, :y :function, :colour :function}}

### 2024-02-04 docs/projects/noj/ml.qmd
Noj -rerendered

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8908     -0.2103      0.0371      0.2256      0.8160

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.0708     0.3356     6.1706     0.0000 ***
sepal-width         0.5954     0.0889     6.6968     0.0000 ***
petal-length        0.6671     0.0715     9.3273     0.0000 ***
petal-width        -0.4532     0.1618    -2.8002     0.0062 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3363 on 96 degrees of freedom
Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7870     -0.2330      0.0191      0.1918      0.8921

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.8173     0.3337     5.4454     0.0000 ***
sepal-width         0.6625     0.0869     7.6273     0.0000 ***
petal-length        0.7158     0.0749     9.5532     0.0000 ***
petal-width        -0.5929     0.1640    -3.6144     0.0005 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3308 on 96 degrees of freedom
Multiple R-squared: 0.8280,    Adjusted R-squared: 0.8227
F-statistic: 154.0902 on 4 and 96 DF,  p-value: 1.435e-36
